Panel Seminars

### 2021-11-05 index.Rmd

* [Choosing a population genomics sequencing approach](WGS_intro.html)  
* [Whole Genome Resequencing](WGS_intro.html)  
* [Reduced Representation Sequencing](RADseq.html)

>>>>

* [Choosing a population genomics sequencing approach](choosing-population-genetics.html)  
* [Whole Genome Resequencing](WGS_intro.html)  
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](poolseq.html)
